Open-Set Domain Adaptation through Self-Supervision

### 2022-02-12 paper/main.tex
added cit file

In \cite{bendale2015open}, OpenMax was proposed as an alternative to the SoftMax operator using 
a statistical method apportion class probabilities to the open-set class. 
A k + 1 classifier for a k class problem was used where the extra class was treated
as the open-set class.

@@

\textbf{Self-supervised Learning}
The emerging field of self-supervised learning uses the machinery of supervised 
learning on problems where external supervision is not available. 
The idea is to use data itself as supervision for auxiliary (also called “pretext”) 
tasks that learn deep feature representations which will hopefully be informative 
for downstream “real” tasks.
Many such auxiliary tasks have been proposed in the literature, including
image colorization \cite{zhang2016colorful,larsson2017learning}, patch location 
prediction \cite{doersch2016unsuperviseddoersch2017multitask},
image jigsaw puzzle [\cite{noroozi2017unsupervised}, image inpainting \cite{pathak2016context},
contrastive learning \cite{oord2019representation}, geometric transformations \cite{dosovitskiy2015discriminative}. Another geometric 
transformation task is rotation recognition \cite{OldROS}, where input images
are rotated by multiples of 90° and the network is trained to predict the rotation
angle pf each image. This pretext task has been successfully used for both anomaly
detection \cite{golan2018deep} and closed-set domain adaptation \cite{selfsupxu}

@@

{\it Multi-head rotation classifier:}
alternatively, 
instead of having a single rotation head predicting the rotation of a sample regardless of its semantic class, 
we also try using a different head for each known class $\in \mathcal{C}_s$, each one responsible of predicting the rotation
of the images belonging to that semantic class.
This variation can mitigate the problem of trying to predict the rotation of a larger number
of semantic classes. Infact, as the number of semantic classes grows,
the problem of predicting the relative orientation becomes more difficult.
The application of the rotation recognition pre-text task allows to effectively favor and force the model to learn
domain-independent patterns, which are crucial to perform the novelty detection in a cross-domain fashion and, moreover,
to successfully perform the domain alignment.
To provide an explanation of why this applies, we can think that a rotation classifier needs to focus on discriminative patterns to
successfully perform the rotation predictions, such as shapes, edges, and high-level object relative position like the position of the eyes
w.r.t nose.
The method and its effectiveness is further illustrated in \cite{OldROS}. 
We will further discuss possible improvements and variants in {\bf PLEASE COMPLETE}.

@@

\section{Future Work}

>>>>

@@

\textbf{Self-supervised Learning}
The emerging field of self-supervised learning uses the machinery of supervised 
learning on problems where external supervision is not available. 
The idea is to use data itself as supervision for auxiliary (also called “pretext”) 
tasks that learn deep feature representations which will hopefully be informative 
for downstream “real” tasks.
Many such auxiliary tasks have been proposed in the literature, including
image colorization \cite{zhang2016colorful,larsson2017learning}, patch location 
prediction \cite{doersch2016unsupervised, doersch2017multitask},
image jigsaw puzzle [\cite{noroozi2017unsupervised}, image inpainting \cite{pathak2016context},
contrastive learning \cite{oord2019representation}, geometric transformations \cite{dosovitskiy2015discriminative}. Another geometric 
transformation task is rotation recognition \cite{OldROS}, where input images
are rotated by multiples of 90° and the network is trained to predict the rotation
angle pf each image. This pretext task has been successfully used for both anomaly
detection \cite{golan2018deep} and closed-set domain adaptation \cite{selfsupxu}

@@

{\it Multi-head rotation classifier:}
alternatively, 
instead of having a single rotation head predicting the rotation of a sample regardless of its semantic class, 
we also try using a different head for each known class $\in \mathcal{C}_s$, each one responsible of predicting the rotation
of the images belonging to that semantic class.
This variation can mitigate the problem of trying to predict the rotation of a larger number
of semantic classes. Infact, as the number of semantic classes grows,
the problem of predicting the relative orientation becomes more difficult.
The application of the rotation recognition pre-text task allows to effectively favor and force the model to learn
domain-independent patterns, which are crucial to perform the novelty detection in a cross-domain fashion and, moreover,
to successfully perform the domain alignment.
To provide an explanation of why this applies, we can think that a rotation classifier needs to focus on discriminative patterns to
successfully perform the rotation predictions, such as shapes, edges, and high-level object relative position like the position of the eyes
w.r.t nose.
The method and its effectiveness is further illustrated in \cite{OldROS},
and further improvements will be discussed in \ref{sec:future_work}.

@@

\section{Future Work}
\label{sec:future_work}
